A Switching Planner for Combined Task and Observation Planning

### 2010-11-22 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
Richard missed some of my changes...
 - Charles

Because $\state_0$ is abstract, and because actions can have
preconditions that are not uniformly true in the underlying
(resp. abstract) belief-state, we must make two further adjustments to
the problem posed to the sequential planner. First, if
$\action\in\actions$ has a precondition that is not true with
probability $1$, then before it is executed blindly, the sequential
continual planning switches to a decision-theoretic mode, discussed in
detail below. Overall, by scheduling $\action$ the sequential planner
makes a naive assumption about the possibility of the agent eventually
committing ---for the purpose of the current task--- to the truth
values of specific state propositions. Second, if the truth value of
$\prop$ is not known, and no assumption is made about it in the
current abstract state, then if $\prop \in \poss(\action)$ we have
that action $\action$ is not applicable.

@@

\noindent which is equal to the maximal contribution a trace of the plan can
make to Eq~\ref{eq:expectedvalue}. In other words, writing $V_i$ for
the value of the $i^{th}$ trace of the plan expressed in $s_0, a_0,
s_1, a_1,.., s_N$, we have:

\[
V^* = \arg\min_{V_i} \Expect \bigg{[} 
\sum_{t=0}^{N}  \reward(\bstate_t) \mid \pp{PLAN}, \bstate = \bstate_0
\bigg{]} - V_i
\]

>>>>

Because $\state_0$ is abstract, and because actions can have
preconditions that are not uniformly true in the underlying
(resp. abstract) belief-state, we must make two further adjustments to
the problem posed to the sequential planner. First, if
$\action\in\actions$ has a precondition that is not true with
probability $1$, then before it is executed blindly, the sequential
continual planning switches to a decision-theoretic mode, discussed in
detail below. Overall, by scheduling $\action$ the sequential planner
makes a naive assumption about the possibility of the agent eventually
``committing'' to the truth values of specific state
propositions. Thus, the role of decision-theoretic plans is to verify
the validity of assumptions about the runtime state in sequential
planning. Second, if the truth value of $\prop$ is not known, and no
assumption is made about it in the current abstract state, then if
$\prop \in
\poss(\action)$ we have that action $\action$ is not applicable.

%% Because $\state_0$ is abstract, and because actions can have
%% preconditions that are not uniformly true in the underlying
%% (resp. abstract) belief-state, we must make two further adjustments to
%% the problem posed to the sequential planner. First, if
%% $\action\in\actions$ has a precondition that is not true with
%% probability $1$, then before it is executed blindly, the sequential
%% continual planning switches to a decision-theoretic mode, discussed in
%% detail below. Overall, by scheduling $\action$ the sequential planner
%% makes a naive assumption about the possibility of the agent eventually
%% committing ---for the purpose of the current task--- to the truth
%% values of specific state propositions. Second, if the truth value of
%% $\prop$ is not known, and no assumption is made about it in the
%% current abstract state, then if $\prop \in \poss(\action)$ we have
%% that action $\action$ is not applicable.

@@

\noindent which is equal to the maximal contribution a trace of the plan can
make to Eq~\ref{eq:expectedvalue}. In other words, writing $V_i$ for
the value of the $i^{th}$ trace of the plan expressed in $s_0, a_0,
s_1, a_1,.., s_N$, we have

\[
V^* = \arg\min_{V_i} \Expect \bigg{[} 
\sum_{t=0}^{N}  \reward(\bstate_t) \mid \pp{PLAN}, \bstate_0
\bigg{]} - V_i.
\]
